---
title: "CH R01 jan2023"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: united
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE,
                      cache = FALSE,
                      fig.align='center'
                      )
```

```{r library}
library(tidyverse)
library(ggplot2)
library(gtsummary)
library(survival)
library(survminer)
theme_gtsummary_compact()
theme_set(theme_classic())
```

```{r load}
germline_data <- read_rds(paste0(here::here(), "/germline_data.rds"))
```

<br>

# I. Data exploration
<div class = "row">
<div class = "col-md-5">
```{r}
germline_data %>% 
  mutate(Whole = "patients with WES") %>% 
  select(age_at_diagnosis, age_at_germline,
         sex, race, ethnicity, Whole, 
         disease_type_conformed,
         stage,
         drugs_ever, radiation_ever, sct_ever,
         CH_status,
         vital_status, os_event
         ) %>%
  tbl_summary(by = Whole, 
              type = list(c(drugs_ever, radiation_ever,
                            sct_ever, os_event) ~ "categorical"),
              label = list(age_at_germline ~ "Age at blood"),
              # sort = list(everything() ~ "frequency"),
              # statistic = list(year_at_dx2 ~ "{mean} ({min} - {max})"),
              digits = list(age_at_germline ~ 2)#,
              # missing = "no"
              ) %>% 
  bold_labels()
```
</div>

<div class = "col-md-7">
```{r}
p <- qplot(x =age_at_germline, data=subset(germline_data,!is.na(age_at_germline)), fill=after_stat(count), geom="histogram") 
p + scale_fill_viridis_c(
  alpha = 1,
  begin = 0,
  end = 1,
  direction = 1,
  option = "D",
  values = NULL,
  space = "Lab",
  na.value = "grey50",
  guide = "colourbar",
  aesthetics = "fill"
) +
  theme_minimal(base_size = 16) +
  labs(x="Age at Blood", y="Number of Patient", title="Repartition of Age at Blood in Avatar")
```
</div>
</div>

```{r}
germline_data %>% 
  mutate(Whole = "patients with WES") %>% 
  select(age_at_germline, sex, race, ethnicity, 
         disease_type_conformed,
         stage,
         drugs_ever, radiation_ever, sct_ever,
         CH_status,
         vital_status, os_event
         ) %>%
  tbl_summary(by = disease_type_conformed, 
              type = list(c(drugs_ever, radiation_ever,
                            sct_ever, os_event) ~ "categorical"),
              label = list(age_at_germline ~ "Age at blood"),
              # sort = list(everything() ~ "frequency"),
              # statistic = list(year_at_dx2 ~ "{mean} ({min} - {max})"),
              digits = list(age_at_germline ~ 2)#,
              # missing = "no"
              ) %>% 
  bold_labels() %>% 
  add_p() %>% bold_p(t=0.05)
```
<br>

# II. Age Distribution in Disparities

## Race
```{r}
p <- ggplot(germline_data %>% filter(!is.na(race)), 
            aes(x=race, y=age_at_germline)) + 
  geom_boxplot() + 
  theme_classic() +
  labs(x=NULL, y="Age at Blood", title="Age of Blood Distribution")
p + geom_jitter(shape=16, position=position_jitter(0.2)) +
  facet_wrap(.~ disease_type_conformed)
```

## Ethnicity
```{r}
p <- ggplot(germline_data %>% filter(!is.na(ethnicity)), 
            aes(x=ethnicity, y=age_at_germline)) + 
  geom_boxplot() + 
  theme_classic() +
  labs(x=NULL, y="Age at Blood", title="Age of Blood Distribution")
p + geom_jitter(shape=16, position=position_jitter(0.2)) +
  facet_wrap(.~ disease_type_conformed)
```

# III. CH
## Table by CH stratified by cancer
```{r}
germline_data %>% 
  mutate(Whole = "patients with WES") %>% 
  select(age_at_germline, sex, race, ethnicity, 
         disease_type_conformed,
         stage,
         drugs_ever, radiation_ever, sct_ever,
         CH_status,
         vital_status, os_event
         ) %>%
  tbl_summary(by = CH_status, 
              type = list(c(drugs_ever, radiation_ever,
                            sct_ever, os_event) ~ "categorical"),
              label = list(age_at_germline ~ "Age at blood"),
              # sort = list(everything() ~ "frequency"),
              # statistic = list(year_at_dx2 ~ "{mean} ({min} - {max})"),
              digits = list(age_at_germline ~ 2)#,
              # missing = "no"
              ) %>% 
  bold_labels() %>% 
  add_p() %>% bold_p(t=0.05)
```

```{r}
tbl1 <- germline_data %>% 
  filter(disease_type_conformed == "BRE - Breast Cancer") %>% 
  mutate(Whole = "patients with WES") %>% 
  select(age_at_germline, sex, race, ethnicity, 
         stage,
         drugs_ever, radiation_ever, sct_ever,
         CH_status,
         vital_status, os_event
         ) %>%
  tbl_summary(by = CH_status, 
              type = list(c(drugs_ever, radiation_ever,
                            sct_ever, os_event) ~ "categorical"),
              label = list(age_at_germline ~ "Age at blood"),
              # sort = list(everything() ~ "frequency"),
              # statistic = list(year_at_dx2 ~ "{mean} ({min} - {max})"),
              digits = list(age_at_germline ~ 2)#,
              # missing = "no"
              ) %>% 
  bold_labels() %>% 
  add_p() %>% bold_p(t=0.05)
tbl2 <- germline_data %>% 
  filter(disease_type_conformed == "GYN - Ovarian Cancer") %>% 
  mutate(Whole = "patients with WES") %>% 
  select(age_at_germline, sex, race, ethnicity, 
         stage,
         drugs_ever, radiation_ever, sct_ever,
         CH_status,
         vital_status, os_event
         ) %>%
  tbl_summary(by = CH_status, 
              type = list(c(drugs_ever, radiation_ever,
                            sct_ever, os_event) ~ "categorical"),
              label = list(age_at_germline ~ "Age at blood"),
              # sort = list(everything() ~ "frequency"),
              # statistic = list(year_at_dx2 ~ "{mean} ({min} - {max})"),
              digits = list(age_at_germline ~ 2)#,
              # missing = "no"
              ) %>% 
  bold_labels() %>% 
  add_p() %>% bold_p(t=0.05)
tbl3 <- germline_data %>% 
  filter(disease_type_conformed == "THO - Lung Cancer") %>% 
  mutate(Whole = "patients with WES") %>% 
  select(age_at_germline, sex, race, ethnicity, 
         stage,
         drugs_ever, radiation_ever, sct_ever,
         CH_status,
         vital_status, os_event
         ) %>%
  tbl_summary(by = CH_status, 
              type = list(c(drugs_ever, radiation_ever,
                            sct_ever, os_event) ~ "categorical"),
              label = list(age_at_germline ~ "Age at blood"),
              # sort = list(everything() ~ "frequency"),
              # statistic = list(year_at_dx2 ~ "{mean} ({min} - {max})"),
              digits = list(age_at_germline ~ 2)#,
              # missing = "no"
              ) %>% 
  bold_labels() %>% 
  add_p() %>% bold_p(t=0.05)
tbl_merge(list(tbl1, tbl2, tbl3), tab_spanner = c("Breast Cancer", "Ovarian Cancer", "Lung Cancer"))
```

## Plots age by CH stratified by cancer
```{r}
p <- ggplot(germline_data %>% filter(!is.na(CH_status)), 
            aes(x=CH_status, y=age_at_germline)) + 
  geom_boxplot() + 
  theme_classic() +
  labs(x=NULL, y="Age at Blood", title="Age of Blood Distribution")
p + geom_jitter(shape=16, position=position_jitter(0.2))

p <- ggplot(germline_data %>% filter(!is.na(CH_status)), 
            aes(x=CH_status, y=age_at_germline)) + 
  geom_boxplot() + 
  theme_classic() +
  labs(x=NULL, y="Age at Blood", title="Age of Blood Distribution")
p + geom_jitter(shape=16, position=position_jitter(0.2)) +
  facet_wrap(.~ disease_type_conformed)
```
<br>

***
<br>

# IV. Survivals
## By Cancer
```{r, fig.height = 7}
mysurv <- Surv(time = germline_data$os_time, event = germline_data$os_event)
myplot <- survfit(mysurv~disease_type_conformed, data = germline_data)
ggsurvplot(myplot, data = germline_data,
           title = "OS from date of blood sample",
           font.main = c(20, "bold", "black"),
           font.x = c(16, "bold", "black"),
           font.y = c(16, "bold", "black"),
           font.legend = c(16, "bold", "black"),
           font.tickslab = c(14, "bold", "black"),
           size = 1.5,
           
           xlab = "Time (years)", 
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           # palette = c("#03051AFF", "blue", "red"),
           pval = TRUE,
           pval.coord = c(0, 0.08),
           conf.int = FALSE,
           # Censor
           censor = TRUE,
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(14, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(14, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black")),
)+ guides(colour = guide_legend(nrow = 3))

tbl1 <- germline_data %>% 
  select(race, ethnicity, age_at_germline, sex, stage, disease_type_conformed,
         drugs_ever, radiation_ever) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = germline_data$os_time,
                             event = germline_data$os_event)),
                   exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% 
  add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <- coxph(Surv(time = germline_data$os_time,
                   event = germline_data$os_event) ~ 
                race + ethnicity + age_at_germline + sex + stage + 
                disease_type_conformed +
                drugs_ever + radiation_ever, 
              data =  germline_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
If I remove sex and drugs_ever
```{r}
tbl1 <- germline_data %>%
  select(race, ethnicity, age_at_germline, stage, disease_type_conformed,
         radiation_ever) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = germline_data$os_time,
                             event = germline_data$os_event)),
                   exponentiate = TRUE) %>%
  bold_p(t = .05) %>% add_nevent(location = "level") %>%
  add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <- coxph(Surv(time = germline_data$os_time,
                   event = germline_data$os_event) ~
                race + ethnicity + age_at_germline + stage +
                disease_type_conformed +
                radiation_ever,
              data =  germline_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```

## Startified by cancer

### Breast cancer
```{r, fig.height = 7}
breast_surv <- germline_data %>% 
  filter(disease_type_conformed == "BRE - Breast Cancer")

tbl1 <- breast_surv %>% 
  select(race, ethnicity, age_at_germline, stage,
         drugs_ever, radiation_ever) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = breast_surv$os_time,
                             event = breast_surv$os_event)),
                   exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% 
  add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <- coxph(Surv(time = breast_surv$os_time,
                   event = breast_surv$os_event) ~ 
                race + ethnicity + age_at_germline + stage + 
                radiation_ever, 
              data =  breast_surv) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```

### Ovarian Cancer
```{r, fig.height = 7}
ovarian_surv <- germline_data %>% 
  filter(disease_type_conformed == "GYN - Ovarian Cancer")

tbl1 <- ovarian_surv %>% 
  select(race, ethnicity, age_at_germline, stage,
         drugs_ever, radiation_ever) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = ovarian_surv$os_time,
                             event = ovarian_surv$os_event)),
                   exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% 
  add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <- coxph(Surv(time = ovarian_surv$os_time,
                   event = ovarian_surv$os_event) ~ 
                race + age_at_germline + stage + 
                radiation_ever, 
              data =  ovarian_surv) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```

### Lung Cancer
<!-- The factor that gave infinite HR were removed from the multivariable analysis. I also had to combine stage categories. -->
```{r, fig.height = 7}
lung_surv <- germline_data #%>%
  # filter(disease_type_conformed == "THO - Lung Cancer") %>%
  # mutate(stage = case_when(
  #   stage == "0-I"        ~ "0-I",
  #   TRUE                  ~ "II-IV"
  # ))

tbl1 <- lung_surv %>%
  select(race, ethnicity, age_at_germline, sex, stage,
         drugs_ever, radiation_ever) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = lung_surv$os_time,
                             event = lung_surv$os_event)),
                   exponentiate = TRUE) %>%
  bold_p(t = .05) %>% add_nevent(location = "level") %>%
  add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <- coxph(Surv(time = lung_surv$os_time,
                   event = lung_surv$os_event) ~
                race + ethnicity + age_at_germline + sex + stage +
                drugs_ever + radiation_ever,
              data =  lung_surv) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
If remove sex, drugs_ever
```{r}
tbl1 <- lung_surv %>%
  select(race, ethnicity, age_at_germline, stage,
         radiation_ever) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = lung_surv$os_time,
                             event = lung_surv$os_event)),
                   exponentiate = TRUE) %>%
  bold_p(t = .05) %>% add_nevent(location = "level") %>%
  add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <- coxph(Surv(time = lung_surv$os_time,
                   event = lung_surv$os_event) ~
                race + ethnicity + age_at_germline + stage +
                radiation_ever,
              data =  lung_surv) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```

## By CH
### Overall
```{r, fig.height = 7}
mysurv <- Surv(time = germline_data$os_time, event = germline_data$os_event)
myplot <- survfit(mysurv~CH_status, data = germline_data)
ggsurvplot(myplot, data = germline_data,
           title = "OS from date of blood sample",
           font.main = c(20, "bold", "black"),
           font.x = c(16, "bold", "black"),
           font.y = c(16, "bold", "black"),
           font.legend = c(16, "bold", "black"),
           font.tickslab = c(14, "bold", "black"),
           size = 1.5,

           xlab = "Time (years)",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           palette = c("blue", "red"),
           pval = TRUE,
           pval.coord = c(0, 0.08),
           conf.int = FALSE,
           # Censor
           censor = TRUE,
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(14, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(14, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black")),
)+ guides(colour = guide_legend(nrow = 3))

tbl1 <- germline_data %>%
  select(race, ethnicity, age_at_germline, sex, stage, disease_type_conformed,
         drugs_ever, radiation_ever, CH_status) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = germline_data$os_time,
                             event = germline_data$os_event)),
                   exponentiate = TRUE) %>%
  bold_p(t = .05) %>% add_nevent(location = "level") %>%
  add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <- coxph(Surv(time = germline_data$os_time,
                   event = germline_data$os_event) ~
                race + ethnicity + age_at_germline + sex + stage +
                disease_type_conformed +
                drugs_ever + radiation_ever + CH_status,
              data =  germline_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```

If I remove drugs_ever and sex
```{r}
tbl1 <- germline_data %>%
  select(race, ethnicity, age_at_germline, stage, disease_type_conformed,
         radiation_ever, CH_status) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = germline_data$os_time,
                             event = germline_data$os_event)),
                   exponentiate = TRUE) %>%
  bold_p(t = .05) %>% add_nevent(location = "level") %>%
  add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <- coxph(Surv(time = germline_data$os_time,
                   event = germline_data$os_event) ~
                race + ethnicity + age_at_germline + stage +
                disease_type_conformed +
                radiation_ever + CH_status,
              data =  germline_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```


### Startified by cancer
#### Breast
```{r, fig.height = 7}
breast_data <- germline_data %>%
    filter(disease_type_conformed == "BRE - Breast Cancer")
mysurv <- Surv(time = breast_data$os_time, event = breast_data$os_event)
myplot <- survfit(mysurv~CH_status, data = breast_data)
ggsurvplot(myplot, data = breast_data,
           title = "OS from date of blood sample",
           font.main = c(20, "bold", "black"),
           font.x = c(16, "bold", "black"),
           font.y = c(16, "bold", "black"),
           font.legend = c(16, "bold", "black"),
           font.tickslab = c(14, "bold", "black"),
           size = 1.5,

           xlab = "Time (years)",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           palette = c("blue", "red"),
           pval = TRUE,
           pval.coord = c(0, 0.08),
           conf.int = FALSE,
           # Censor
           censor = TRUE,
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(14, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(14, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black")),
)+ guides(colour = guide_legend(nrow = 3))

tbl1 <- breast_data %>%
  select(race, ethnicity, age_at_germline, stage,
         drugs_ever, radiation_ever, CH_status) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = breast_data$os_time,
                             event = breast_data$os_event)),
                   exponentiate = TRUE) %>%
  bold_p(t = .05) %>% add_nevent(location = "level") %>%
  add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <- coxph(Surv(time = breast_data$os_time,
                   event = breast_data$os_event) ~
                race + ethnicity + age_at_germline + stage +
                drugs_ever + radiation_ever + CH_status,
              data =  breast_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
No event in CH patients

#### Ovarian
```{r, fig.height = 7}
ovarian_data <- germline_data %>%
  filter(disease_type_conformed == "GYN - Ovarian Cancer")
mysurv <- Surv(time = ovarian_data$os_time, event = ovarian_data$os_event)
myplot <- survfit(mysurv~CH_status, data = ovarian_data)
ggsurvplot(myplot, data = ovarian_data,
           title = "OS from date of blood sample",
           font.main = c(20, "bold", "black"),
           font.x = c(16, "bold", "black"),
           font.y = c(16, "bold", "black"),
           font.legend = c(16, "bold", "black"),
           font.tickslab = c(14, "bold", "black"),
           size = 1.5,

           xlab = "Time (years)",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           palette = c("blue", "red"),
           pval = TRUE,
           pval.coord = c(0, 0.08),
           conf.int = FALSE,
           # Censor
           censor = TRUE,
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(14, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(14, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black")),
)+ guides(colour = guide_legend(nrow = 3))

tbl1 <- ovarian_data %>%
  select(race, ethnicity, age_at_germline, stage,
         drugs_ever, radiation_ever, CH_status) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = ovarian_data$os_time,
                             event = ovarian_data$os_event)),
                   exponentiate = TRUE) %>%
  bold_p(t = .05) %>% add_nevent(location = "level") %>%
  add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <- coxph(Surv(time = ovarian_data$os_time,
                   event = ovarian_data$os_event) ~
                race + ethnicity + age_at_germline + stage +
                drugs_ever + radiation_ever + CH_status,
              data =  ovarian_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
If I remove ethnicity and drugs_ever, combine stage, remove race
```{r}
ovarian_data <- ovarian_data %>%
  mutate(stage = case_when(
    stage == "0-I" |
    stage == "II"         ~ "0-II",
    TRUE                  ~ as.character(stage)
  ))
tbl1 <- ovarian_data %>%
  select(age_at_germline, stage,
         radiation_ever, CH_status) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = ovarian_data$os_time,
                             event = ovarian_data$os_event)),
                   exponentiate = TRUE) %>%
  bold_p(t = .05) %>% add_nevent(location = "level") %>%
  add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <- coxph(Surv(time = ovarian_data$os_time,
                   event = ovarian_data$os_event) ~
                age_at_germline + stage +
                radiation_ever + CH_status,
              data =  ovarian_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```


#### Lung
```{r, fig.height = 7}
lung_data <- germline_data %>%
  filter(disease_type_conformed == "THO - Lung Cancer")
mysurv <- Surv(time = lung_data$os_time, event = lung_data$os_event)
myplot <- survfit(mysurv~CH_status, data = lung_data)
ggsurvplot(myplot, data = lung_data,
           title = "OS from date of blood sample",
           font.main = c(20, "bold", "black"),
           font.x = c(16, "bold", "black"),
           font.y = c(16, "bold", "black"),
           font.legend = c(16, "bold", "black"),
           font.tickslab = c(14, "bold", "black"),
           size = 1.5,

           xlab = "Time (years)",
           legend = "top",
           legend.title = "",
           # legend.labs = c("White Non-Hispanic", "Hispanic", "Black"),
           palette = c("blue", "red"),
           pval = TRUE,
           pval.coord = c(0, 0.08),
           conf.int = FALSE,
           # Censor
           censor = TRUE,
           # Add risk table
           tables.height = 0.3,
           risk.table.title = "Risk table",
           risk.table = TRUE,
           risk.table.y.text = FALSE,
           risk.table.fontsize = 4,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(14, "bold", "black"),
                                          font.x = c(14, "bold", "black"),
                                          font.y = c(14, "bold", "transparent"),
                                          font.tickslab = c(14, "bold", "black")),
)+ guides(colour = guide_legend(nrow = 3))

tbl1 <- lung_data %>%
  select(race, ethnicity, age_at_germline, sex, stage,
         drugs_ever, radiation_ever, CH_status) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = lung_data$os_time,
                             event = lung_data$os_event)),
                   exponentiate = TRUE) %>%
  bold_p(t = .05) %>% add_nevent(location = "level") %>%
  add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <- coxph(Surv(time = lung_data$os_time,
                   event = lung_data$os_event) ~
                race + ethnicity + age_at_germline + sex + stage +
                drugs_ever + radiation_ever + CH_status,
              data =  lung_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```
If I remove race, ethnicity, stage, remove drugs
```{r}
tbl1 <- lung_data %>%
  select(age_at_germline, sex, radiation_ever, CH_status) %>%
  tbl_uvregression(method = survival::coxph,
                   y = (Surv(time = lung_data$os_time,
                             event = lung_data$os_event)),
                   exponentiate = TRUE) %>%
  bold_p(t = .05) %>% add_nevent(location = "level") %>%
  add_n(location = "level") %>%
  bold_labels() %>% italicize_levels()
tbl2 <- coxph(Surv(time = lung_data$os_time,
                   event = lung_data$os_event) ~
                age_at_germline + sex +
                radiation_ever + CH_status,
              data =  lung_data) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05)
tbl_merge(list(tbl1, tbl2), tab_spanner = c("**Univariable**", "**Multivariable**"))
```





